When does vapor pressure deficit drive or reduce evapotranspiration?

### 2019-09-06 doc/paper/agu-james-submission-single-file.tex
need to use agu's template for supp material
also I added all of the fluxnet citations to the main mauscript,
per agu's guidelines

%% added by adam
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\appropto}{\mathrel{\vcenter{
      \offinterlineskip\halign{\hfil$##$\cr
        \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

%% added by adam
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\appropto}{\mathrel{\vcenter{
      \offinterlineskip\halign{\hfil$##$\cr
        \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\usepackage{textcomp}

@@

% include all the fluxnet citations I use in the supp material
\nocite{AT-Neu, AU-ASM, AU-ASM, AU-Cpr, AU-DaP, AU-DaS, AU-Dry, AU-Gin,
  AU-How, AU-Gin, AU-DaP, AU-Tum, AU-Whr, AU-Wom, BE-Lon, BE-Vie,
  BR-Sa3, CA-Qfo, CA-SF1, CA-SF1, CH-Cha, CH-Dav, CH-Fru, DE-Geb,
  DE-Gri, DE-Hai, DE-Gri, DE-Lkb, DE-Seh, DE-Tha, DK-Sor, FI-Hyy,
  FI-Sod, FR-Gri, FR-LBr, IT-Col, IT-Cpz, IT-Lav, IT-MBo, IT-Noe,
  IT-Ren, IT-Ro2, IT-SRo, IT-Tor, NL-Loo, RU-Fyo, US-AR1, US-AR1,
  US-ARM, US-Blo, US-KS2, US-MMS, US-Me2, US-NR1, US-Ne1, US-Ne1,
  US-Ne1, US-SRG, US-SRM, US-Syv, US-Ton, US-Var, US-WCr, US-Wkg,
  ZA-Kru, ZM-Mon}

@@

\bibitem [\protect \citeauthoryear {%
Anthoni%
\ \protect \BOthers {.}}{%
Anthoni%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2004}}%
}]{%
DE-Geb}
\APACinsertmetastar {%
DE-Geb}%
\begin{APACrefauthors}%
Anthoni, P\BPBI M.%
, Knohl, A.%
, Rebmann, C.%
, Freibauer, A.%
, Mund, M.%
, Ziegler, W.%
\BDBL {}Schulze, E\BHBI D.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2004}{dec}{}.
\newblock
{\BBOQ}\APACrefatitle {Forest and agricultural land-use-dependent {CO}2
  exchange in {T}huringia, {G}ermany} {Forest and agricultural
  land-use-dependent {CO}2 exchange in {T}huringia, {G}ermany}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Global Change Biology}{10}{12}{2005--2019}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1111%2Fj.1365-2486.2004.00863.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-2486.2004.00863.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Archibald%
\ \protect \BOthers {.}}{%
Archibald%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2009}}%
}]{%
ZA-Kru}
\APACinsertmetastar {%
ZA-Kru}%
\begin{APACrefauthors}%
Archibald, S\BPBI A.%
, Kirton, A.%
, van~der Merwe, M\BPBI R.%
, Scholes, R\BPBI J.%
, Williams, C\BPBI A.%
\BCBL {}\ \BBA {} Hanan, N.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2009}{feb}{}.
\newblock
{\BBOQ}\APACrefatitle {Drivers of inter-annual variability in Net Ecosystem
  Exchange in a semi-arid savanna ecosystem, {S}outh {A}frica} {Drivers of
  inter-annual variability in net ecosystem exchange in a semi-arid savanna
  ecosystem, {S}outh {A}frica}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Biogeosciences}{6}{2}{251--266}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.5194%2Fbg-6-251-2009}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.5194/bg-6-251-2009} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Aubinet%
\ \protect \BOthers {.}}{%
Aubinet%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2001}}%
}]{%
BE-Vie}
\APACinsertmetastar {%
BE-Vie}%
\begin{APACrefauthors}%
Aubinet, M.%
, Chermanne, B.%
, Vandenhaute, M.%
, Longdoz, B.%
, Yernaux, M.%
\BCBL {}\ \BBA {} Laitat, E.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2001}{jul}{}.
\newblock
{\BBOQ}\APACrefatitle {Long term carbon dioxide exchange above a mixed forest
  in the {B}elgian {A}rdennes} {Long term carbon dioxide exchange above a mixed
  forest in the {B}elgian {A}rdennes}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest Meteorology}{108}{4}{293--315}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fs0168-1923%2801%2900244-1}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/s0168-1923(01)00244-1} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Baldocchi%
\ \protect \BOthers {.}}{%
Baldocchi%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2010}}%
}]{%
US-Ton}
\APACinsertmetastar {%
US-Ton}%
\begin{APACrefauthors}%
Baldocchi, D.%
, Chen, Q.%
, Chen, X.%
, Ma, S.%
, Miller, G.%
, Ryu, Y.%
\BDBL {}Battles, J.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2010}{nov}{}.
\newblock
{\BBOQ}\APACrefatitle {The Dynamics of Energy, Water, and Carbon Fluxes in a
  Blue Oak ({Q}uercus douglasii) Savanna in {C}alifornia} {The dynamics of
  energy, water, and carbon fluxes in a blue oak ({Q}uercus douglasii) savanna
  in {C}alifornia}.{\BBCQ}
\newblock
\BIn{} \APACrefbtitle {Ecosystem Function in {S}avannas} {Ecosystem function in
  {S}avannas}\ (\BPGS\ 135--151).
\newblock
\APACaddressPublisher{}{{CRC} Press}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1201%2Fb10275-10} \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1201/b10275-10} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Berbigier%
, Bonnefond%
\BCBL {}\ \BBA {} Mellmann%
}{%
Berbigier%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2001}}%
}]{%
FR-LBr}
\APACinsertmetastar {%
FR-LBr}%
\begin{APACrefauthors}%
Berbigier, P.%
, Bonnefond, J\BHBI M.%
\BCBL {}\ \BBA {} Mellmann, P.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2001}{jun}{}.
\newblock
{\BBOQ}\APACrefatitle {{CO}2 and water vapour fluxes for 2 years above
  {E}uroflux forest site} {{CO}2 and water vapour fluxes for 2 years above
  {E}uroflux forest site}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest Meteorology}{108}{3}{183--197}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fs0168-1923%2801%2900240-4}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/s0168-1923(01)00240-4} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Bergeron%
\ \protect \BOthers {.}}{%
Bergeron%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2007}}%
}]{%
CA-Qfo}
\APACinsertmetastar {%
CA-Qfo}%
\begin{APACrefauthors}%
Bergeron, O.%
, Margolis, H\BPBI A.%
, Black, T\BPBI A.%
, Coursolle, C.%
, Dunn, A\BPBI L.%
, Barr, A\BPBI G.%
\BCBL {}\ \BBA {} Wofsy, S\BPBI C.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2007}{jan}{}.
\newblock
{\BBOQ}\APACrefatitle {Comparison of carbon dioxide fluxes over three boreal
  black spruce forests in {C}anada} {Comparison of carbon dioxide fluxes over
  three boreal black spruce forests in {C}anada}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Global Change Biology}{13}{1}{89--107}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1111%2Fj.1365-2486.2006.01281.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-2486.2006.01281.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Beringer%
, Hutley%
, Hacker%
, Neininger%
\BCBL {}\ \BBA {} U%
}{%
Beringer%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2011}}%
}]{%
AU-DaP}
\APACinsertmetastar {%
AU-DaP}%
\begin{APACrefauthors}%
Beringer, J.%
, Hutley, L\BPBI B.%
, Hacker, J\BPBI M.%
, Neininger, B.%
\BCBL {}\ \BBA {} U, K\BPBI T\BPBI P.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2011}{nov}{}.
\newblock
{\BBOQ}\APACrefatitle {Patterns and processes of carbon, water and energy
  cycles across northern {A}ustralian landscapes: From point to region}
  {Patterns and processes of carbon, water and energy cycles across northern
  {A}ustralian landscapes: From point to region}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest
  Meteorology}{151}{11}{1409--1416}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fj.agrformet.2011.05.003}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/j.agrformet.2011.05.003} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Beringer%
\ \protect \BOthers {.}}{%
Beringer%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2016}}%
}]{%
AU-Gin}
\APACinsertmetastar {%
AU-Gin}%
\begin{APACrefauthors}%
Beringer, J.%
, Hutley, L\BPBI B.%
, McHugh, I.%
, Arndt, S\BPBI K.%
, Campbell, D.%
, Cleugh, H\BPBI A.%
\BDBL {}Wardlaw, T.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2016}{oct}{}.
\newblock
{\BBOQ}\APACrefatitle {{An introduction to the Australian and New Zealand flux
  tower network - OzFlux}} {{An introduction to the Australian and New Zealand
  flux tower network - OzFlux}}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Biogeosciences}{13}{21}{5895--5916}.
\newblock
\begin{APACrefURL} \url{http://www.biogeosciences.net/13/5895/2016/
  https://doi.org/10.5194 https://doi.org/10.5194{\%}2Fbg-13-5895-2016}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.5194/bg-13-5895-2016} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Beringer%
, Hutley%
, Tapper%
\BCBL {}\ \BBA {} Cernusak%
}{%
Beringer%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2007}}%
}]{%
AU-How}
\APACinsertmetastar {%
AU-How}%
\begin{APACrefauthors}%
Beringer, J.%
, Hutley, L\BPBI B.%
, Tapper, N\BPBI J.%
\BCBL {}\ \BBA {} Cernusak, L\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2007}{may}{}.
\newblock
{\BBOQ}\APACrefatitle {Savanna fires and their impact on net ecosystem
  productivity in {N}orth {A}ustralia} {Savanna fires and their impact on net
  ecosystem productivity in {N}orth {A}ustralia}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Global Change Biology}{13}{5}{990--1004}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1111%2Fj.1365-2486.2007.01334.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-2486.2007.01334.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Cernusak%
, Hutley%
, Beringer%
, Holtum%
\BCBL {}\ \BBA {} Turner%
}{%
Cernusak%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2011}}%
}]{%
AU-Dry}
\APACinsertmetastar {%
AU-Dry}%
\begin{APACrefauthors}%
Cernusak, L\BPBI A.%
, Hutley, L\BPBI B.%
, Beringer, J.%
, Holtum, J\BPBI A.%
\BCBL {}\ \BBA {} Turner, B\BPBI L.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2011}{nov}{}.
\newblock
{\BBOQ}\APACrefatitle {Photosynthetic physiology of eucalypts along a
  sub-continental rainfall gradient in northern {A}ustralia} {Photosynthetic
  physiology of eucalypts along a sub-continental rainfall gradient in northern
  {A}ustralia}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest
  Meteorology}{151}{11}{1462--1470}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fj.agrformet.2011.01.006}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/j.agrformet.2011.01.006} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Chiesi%
\ \protect \BOthers {.}}{%
Chiesi%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2005}}%
}]{%
IT-SRo}
\APACinsertmetastar {%
IT-SRo}%
\begin{APACrefauthors}%
Chiesi, M.%
, Maselli, F.%
, Bindi, M.%
, Fibbi, L.%
, Cherubini, P.%
, Arlotta, E.%
\BDBL {}Seufert, G.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2005}{dec}{}.
\newblock
{\BBOQ}\APACrefatitle {Modelling carbon budget of {M}editerranean forests using
  ground and remote sensing measurements} {Modelling carbon budget of
  {M}editerranean forests using ground and remote sensing measurements}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest Meteorology}{135}{1-4}{22--34}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fj.agrformet.2005.09.011}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/j.agrformet.2005.09.011} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Cleverly%
\ \protect \BOthers {.}}{%
Cleverly%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2013}}%
}]{%
AU-ASM}
\APACinsertmetastar {%
AU-ASM}%
\begin{APACrefauthors}%
Cleverly, J.%
, Boulain, N.%
, Villalobos-Vega, R.%
, Grant, N.%
, Faux, R.%
, Wood, C.%
\BDBL {}Eamus, D.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2013}{jul}{}.
\newblock
{\BBOQ}\APACrefatitle {Dynamics of component carbon fluxes in a semi-arid
  {A}cacia woodland, central {A}ustralia} {Dynamics of component carbon fluxes
  in a semi-arid {A}cacia woodland, central {A}ustralia}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Journal of Geophysical Research:
  Biogeosciences}{118}{3}{1168--1185}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1002%2Fjgrg.20101} \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1002/jgrg.20101} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Cook%
\ \protect \BOthers {.}}{%
Cook%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2004}}%
}]{%
US-WCr}
\APACinsertmetastar {%
US-WCr}%
\begin{APACrefauthors}%
Cook, B\BPBI D.%
, Davis, K\BPBI J.%
, Wang, W.%
, Desai, A.%
, Berger, B\BPBI W.%
, Teclaw, R\BPBI M.%
\BDBL {}Heilman, W.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2004}{nov}{}.
\newblock
{\BBOQ}\APACrefatitle {Carbon exchange and venting anomalies in an upland
  deciduous forest in northern {W}isconsin, {USA}} {Carbon exchange and venting
  anomalies in an upland deciduous forest in northern {W}isconsin,
  {USA}}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest
  Meteorology}{126}{3-4}{271--295}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fj.agrformet.2004.06.008}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/j.agrformet.2004.06.008} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Desai%
, Bolstad%
, Cook%
, Davis%
\BCBL {}\ \BBA {} Carey%
}{%
Desai%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2005}}%
}]{%
US-Syv}
\APACinsertmetastar {%
US-Syv}%
\begin{APACrefauthors}%
Desai, A\BPBI R.%
, Bolstad, P\BPBI V.%
, Cook, B\BPBI D.%
, Davis, K\BPBI J.%
\BCBL {}\ \BBA {} Carey, E\BPBI V.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2005}{jan}{}.
\newblock
{\BBOQ}\APACrefatitle {Comparing net ecosystem exchange of carbon dioxide
  between an old-growth and mature forest in the upper {M}idwest, {USA}}
  {Comparing net ecosystem exchange of carbon dioxide between an old-growth and
  mature forest in the upper {M}idwest, {USA}}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest Meteorology}{128}{1-2}{33--55}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fj.agrformet.2004.09.005}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/j.agrformet.2004.09.005} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Dragoni%
\ \protect \BOthers {.}}{%
Dragoni%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2011}}%
}]{%
US-MMS}
\APACinsertmetastar {%
US-MMS}%
\begin{APACrefauthors}%
Dragoni, D.%
, Schmid, H\BPBI P.%
, Wayson, C\BPBI A.%
, Potter, H.%
, Grimmond, C\BPBI S\BPBI B.%
\BCBL {}\ \BBA {} Randolph, J\BPBI C.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2011}{jan}{}.
\newblock
{\BBOQ}\APACrefatitle {Evidence of increased net ecosystem productivity
  associated with a longer vegetated season in a deciduous forest in
  south-central {I}ndiana, {USA}} {Evidence of increased net ecosystem
  productivity associated with a longer vegetated season in a deciduous forest
  in south-central {I}ndiana, {USA}}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Global Change Biology}{17}{2}{886--897}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1111%2Fj.1365-2486.2010.02281.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-2486.2010.02281.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Fischer%
, Billesbach%
, Berry%
, Riley%
\BCBL {}\ \BBA {} Torn%
}{%
Fischer%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2007}}%
}]{%
US-ARM}
\APACinsertmetastar {%
US-ARM}%
\begin{APACrefauthors}%
Fischer, M\BPBI L.%
, Billesbach, D\BPBI P.%
, Berry, J\BPBI A.%
, Riley, W\BPBI J.%
\BCBL {}\ \BBA {} Torn, M\BPBI S.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2007}{oct}{}.
\newblock
{\BBOQ}\APACrefatitle {Spatiotemporal Variations in Growing Season Exchanges of
  {CO}2, {H2O}, and Sensible Heat in Agricultural Fields of the Southern
  {G}reat {P}lains} {Spatiotemporal variations in growing season exchanges of
  {CO}2, {H2O}, and sensible heat in agricultural fields of the southern
  {G}reat {P}lains}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Earth Interactions}{11}{17}{1--21}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1175%2Fei231.1} \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1175/ei231.1} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Galvagno%
\ \protect \BOthers {.}}{%
Galvagno%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2013}}%
}]{%
IT-Tor}
\APACinsertmetastar {%
IT-Tor}%
\begin{APACrefauthors}%
Galvagno, M.%
, Wohlfahrt, G.%
, Cremonese, E.%
, Rossini, M.%
, Colombo, R.%
, Filippa, G.%
\BDBL {}Migliavacca, M.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2013}{apr}{}.
\newblock
{\BBOQ}\APACrefatitle {Phenology and carbon dioxide source/sink strength of a
  subalpine grassland in response to an exceptionally short snow season}
  {Phenology and carbon dioxide source/sink strength of a subalpine grassland
  in response to an exceptionally short snow season}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Environmental Research Letters}{8}{2}{025008}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1088%2F1748-9326%2F8%2F2%2F025008}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1088/1748-9326/8/2/025008} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Garbulsky%
, Pe{\~{n}}uelas%
, Papale%
\BCBL {}\ \BBA {} Filella%
}{%
Garbulsky%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2008}}%
}]{%
IT-Cpz}
\APACinsertmetastar {%
IT-Cpz}%
\begin{APACrefauthors}%
Garbulsky, M\BPBI F.%
, Pe{\~{n}}uelas, J.%
, Papale, D.%
\BCBL {}\ \BBA {} Filella, I.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2008}{dec}{}.
\newblock
{\BBOQ}\APACrefatitle {Remote estimation of carbon dioxide uptake by a
  {M}editerranean forest} {Remote estimation of carbon dioxide uptake by a
  {M}editerranean forest}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Global Change Biology}{14}{12}{2860--2867}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1111%2Fj.1365-2486.2008.01684.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-2486.2008.01684.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Goldstein%
\ \protect \BOthers {.}}{%
Goldstein%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2000}}%
}]{%
US-Blo}
\APACinsertmetastar {%
US-Blo}%
\begin{APACrefauthors}%
Goldstein, A.%
, Hultman, N.%
, Fracheboud, J.%
, Bauer, M.%
, Panek, J.%
, Xu, M.%
\BDBL {}Baugh, W.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2000}{mar}{}.
\newblock
{\BBOQ}\APACrefatitle {Effects of climate variability on the carbon dioxide,
  water, and sensible heat fluxes above a ponderosa pine plantation in the
  {S}ierra {N}evada ({CA})} {Effects of climate variability on the carbon
  dioxide, water, and sensible heat fluxes above a ponderosa pine plantation in
  the {S}ierra {N}evada ({CA})}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest
  Meteorology}{101}{2-3}{113--129}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fs0168-1923%2899%2900168-9}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/s0168-1923(99)00168-9} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Gr{\"u}nwald%
\ \BBA {} Bernhofer%
}{%
Gr{\"u}nwald%
\ \BBA {} Bernhofer%
}{%
{\protect \APACyear {2007}}%
}]{%
DE-Tha}
\APACinsertmetastar {%
DE-Tha}%
\begin{APACrefauthors}%
Gr{\"u}nwald, T.%
\BCBT {}\ \BBA {} Bernhofer, C.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2007}{jul}{}.
\newblock
{\BBOQ}\APACrefatitle {A decade of carbon, water and energy flux measurements
  of an old spruce forest at the {A}nchor {S}tation {T}harandt} {A decade of
  carbon, water and energy flux measurements of an old spruce forest at the
  {A}nchor {S}tation {T}harandt}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Tellus B}{59}{3}{}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.3402%2Ftellusb.v59i3.17000}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.3402/tellusb.v59i3.17000} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Hinko-Najera%
\ \protect \BOthers {.}}{%
Hinko-Najera%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2017}}%
}]{%
AU-Wom}
\APACinsertmetastar {%
AU-Wom}%
\begin{APACrefauthors}%
Hinko-Najera, N.%
, Isaac, P.%
, Beringer, J.%
, van Gorsel, E.%
, Ewenz, C.%
, McHugh, I.%
\BDBL {}Arndt, S\BPBI K.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2017}{}{}.
\newblock
{\BBOQ}\APACrefatitle {{Net ecosystem carbon exchange of a dry temperate
  eucalypt forest}} {{Net ecosystem carbon exchange of a dry temperate eucalypt
  forest}}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Biogeosciences}{14}{16}{3781--3800}.
\newblock
\begin{APACrefURL} \url{https://www.biogeosciences.net/14/3781/2017/}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.5194/bg-14-3781-2017} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Hutley%
, Beringer%
, Isaac%
, Hacker%
\BCBL {}\ \BBA {} Cernusak%
}{%
Hutley%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2011}}%
}]{%
AU-DaS}
\APACinsertmetastar {%
AU-DaS}%
\begin{APACrefauthors}%
Hutley, L\BPBI B.%
, Beringer, J.%
, Isaac, P\BPBI R.%
, Hacker, J\BPBI M.%
\BCBL {}\ \BBA {} Cernusak, L\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2011}{nov}{}.
\newblock
{\BBOQ}\APACrefatitle {A sub-continental scale living laboratory: Spatial
  patterns of savanna vegetation over a rainfall gradient in northern
  {A}ustralia} {A sub-continental scale living laboratory: Spatial patterns of
  savanna vegetation over a rainfall gradient in northern {A}ustralia}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest
  Meteorology}{151}{11}{1417--1428}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1016%2Fj.agrformet.2011.03.002}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1016/j.agrformet.2011.03.002} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Imer%
, Merbold%
, Eugster%
\BCBL {}\ \BBA {} Buchmann%
}{%
Imer%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2013}}%
}]{%
CH-Fru}
\APACinsertmetastar {%
CH-Fru}%
\begin{APACrefauthors}%
Imer, D.%
, Merbold, L.%
, Eugster, W.%
\BCBL {}\ \BBA {} Buchmann, N.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2013}{sep}{}.
\newblock
{\BBOQ}\APACrefatitle {Temporal and spatial variations of soil
  {CO}\textsubscript{2}, {CH}\textsubscript{4} and {N}\textsubscript{2}{O}
  fluxes at three differently managed grasslands} {Temporal and spatial
  variations of soil {CO}\textsubscript{2}, {CH}\textsubscript{4} and
  {N}\textsubscript{2}{O} fluxes at three differently managed
  grasslands}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Biogeosciences}{10}{9}{5931--5945}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.5194%2Fbg-10-5931-2013}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.5194/bg-10-5931-2013} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Irvine%
, Law%
, Martin%
\BCBL {}\ \BBA {} Vickers%
}{%
Irvine%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2008}}%
}]{%
US-Me2}
\APACinsertmetastar {%
US-Me2}%
\begin{APACrefauthors}%
Irvine, J.%
, Law, B\BPBI E.%
, Martin, J\BPBI G.%
\BCBL {}\ \BBA {} Vickers, D.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2008}{dec}{}.
\newblock
{\BBOQ}\APACrefatitle {Interannual variation in soil {CO}2 efflux and the
  response of root respiration to climate and canopy gas exchange in mature
  ponderosa pine} {Interannual variation in soil {CO}2 efflux and the response
  of root respiration to climate and canopy gas exchange in mature ponderosa
  pine}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Global Change Biology}{14}{12}{2848--2859}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1111%2Fj.1365-2486.2008.01682.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-2486.2008.01682.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

@@

\bibitem [\protect \citeauthoryear {%
Moors%
}{%
Moors%
}{%
{\protect \APACyear {2012}}%
}]{%
NL-Loo}
\APACinsertmetastar {%
NL-Loo}%
\begin{APACrefauthors}%
Moors, E.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYear{2012}.
\unskip\
\newblock
\APACrefbtitle {{Water Use of Forests in The Netherlands}} {{Water Use of
  Forests in The Netherlands}}\ \APACtypeAddressSchool {\BUPhD}{}{}.
\unskip\
\newblock
\APACaddressSchool {}{Vrije Universiteit Amsterdam}.
\PrintBackRefs{\CurrentBib}
